Predicting tree failure likelihood for utility risk mitigation via a novel convolutional neural network

### 2021-02-20 docs/manuscript/manuscript.tex

\begin{table}[h!]\small

@@

 % Please add the following required packages to your document preamble:
% \usepackage{booktabs}
% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
% \usepackage{multirow}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{figures/scenario_resolution_performance.png}
    \caption{Performance metrics for each scenario and input resolution instance. Average metrics and confidence intervals (trials, $n=10$) are shown for 10 epochs in each case.}
    \label{fig:sens-overall}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{figures/scenario_resolution_validation_accuracy.png}
    \caption{Mean validation accuracy values with error bars for each scenario and resolution combination.}
    \label{fig:sens-val-acc}
\end{figure}

\begin{table}[h!]\small
    \centering
    \begin{tabular}{ l c r r}\toprule
\bf Scenario & \bf Resolution & \multicolumn{2}{c}{\bf Validation Accuracy}\\
& & Mean & SD \\\midrule
    \texttt{PrPo\_Im} & 64  & 0.96 & 0.04 \\
                      & 128 & 0.96 & 0.05 \\
    \texttt{Pr\_Im}   & 64  & 0.98 & 0.03 \\
                      & 128 & 0.97 & 0.03 \\
    \texttt{Pr\_PoIm} & 64  & 0.96 & 0.04 \\
                      & 128 & 0.97 & 0.04 \\
    \texttt{Pr\_Po\_Im}& 64  & 0.94 & 0.07 \\
                      & 128 & 0.95 & 0.07 \\ \bottomrule
    \end{tabular}
    \caption{Summary validation accuracy (mean and standard deviation) for each scenario and input image resolution training instance. There is no statistically significant difference between the performance for each resolution case under each scenario.}
    \label{tab:meanvalacc}
\end{table}
\subsection{Model visualization and inference}

@@

\section{Acknowledgments}

>>>>

\subsection{Optimal hyperparameters}
The results of the 8 hyperparameters optimized in each of the 12 training instances is shown in \autoref{tab:opt-hyp}.
\begin{table}[ht!]\small

@@

@@

We trained the CNN for each of the 4 classification scenarios. In each scenarios, we also trained on three image resolution sets (64, 108 and 224). The goal was to determine the best performing resolution, given the tradeoff between performance and computational expenditure. Thus, twelve learning instances were generated, using a training-validation ratio of 80:20. In each instance, we performed 10 trials, each consisting of 10 epochs. Validation sets were randomly selected in each trial, but consistent across each of the 12 training instances. The trajectories of the training/validation loss and accuracy are shown in \autoref{fig:sens-overall}. Although the 64-pixel case is the slowest to converge in all scenarios, it appears to have a similar performance with respect to the other two resolutions (128px and 224px).

\begin{figure}[ht]
    \centering
    \includegraphics[width=1.05\textwidth]{scenario_resolution_performance.png}
    \caption{Performance metrics for each scenario and input resolution instance. Average metrics and confidence intervals (trials, $n=10$) are shown for 10 epochs in each case.}
    \label{fig:sens-overall}
\end{figure}

\autoref{fig:sens-val-acc} shows the boxplots of the validation accuracy in all twelve instances ($n=10$).
We further summarize the statistics (mean and standard deviation) of the validation accuracies in \autoref{tab:meanvalacc}.
Using the Welch test for pairwise comparisons of resolution performance within each scenario, we find no statistically significant difference between the validation accuracy for each resolution ($p\ge 0.57$).
\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{figures/scenario_resolution_validation_accuracy_boxplot.png}
    \caption{Boxplots of validation accuracy values with error bars for each scenario and resolution combination. Mean values are depicted as white squares in each box.}
    \label{fig:sens-val-acc}
\end{figure}
\begin{table}[h!]\small
    \centering
    \begin{tabular}{ l c r r}\toprule
\bf Scenario & \bf Resolution & \multicolumn{2}{c}{\bf Validation Accuracy}\\
& & Mean & SD \\\midrule
    \texttt{PrPo\_Im} & 64  & 0.96 & 0.04 \\
                      & 128 & 0.96 & 0.05 \\
                      &224  &      0.96&  0.05  \\ \midrule        
    \texttt{Pr\_Im}   & 64  & 0.98 & 0.03 \\
                      & 128 & 0.97 & 0.03 \\
                      & 224 & 0.97 & 0.03\\\midrule       
    \texttt{Pr\_PoIm} & 64  & 0.96 & 0.04 \\
                      & 128 & 0.97 & 0.04 \\
                      & 224 & 0.97 & 0.04 \\\midrule       
    \texttt{Pr\_Po\_Im}& 64  & 0.94 & 0.07 \\
                      & 128 & 0.95 & 0.07 \\
                      & 224 & 0.95 & 0.06 \\\bottomrule
    \end{tabular}
    \caption{Summary validation accuracy (mean and standard deviation to 2 decimal places) for each scenario and input image resolution training instance. There is no statistically significant difference between the performance for each resolution case under each scenario.}
    \label{tab:meanvalacc}
\end{table}

Given that there was no significant difference in performance among the three resolutions tested, we focus our attention on the 64-px case, in the interest of efficiency. We re-trained the model on all the four scenarios and then evaluated performance on the following validation metrics: average precision, average recall and accuracy.

\subsection{Model visualization and inference}

@@

\section{Acknowledgments}
The authors would like to thank...
